---
output:
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./templates/svm-latex-ms.tex
  html_document:
    highlighting: tango
    keep_md: yes
    self_contained: yes
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: no
    fig_caption: yes
  rticles::springer_article:
title: "Your project title here"
thanks: "Thanks to Steven V Miller for his inspirational template (https://github.com/svmiller/svm-r-markdown-templates)"
author:
- name: Your name
  affiliation: Neurocure Clinical Research Center, Charité Universitätsmedizin Berlin
- name: Someone else's name
  affiliation: Neurocure Clinical Research Center, Charité Universitätsmedizin Berlin
- name: Another person's name
  affiliation: Neurocure Clinical Research Center, Charité Universitätsmedizin Berlin
abstract: "Your abstract here"
keywords: "keywords here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
tables: true
link-citations: yes
bibliography: library.bib
biblio-style: apsr
---

```{r knitr options, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "figs/",
  screenshot.force = FALSE,
  dpi = 1200,
  dev = c("png", "jpeg", "cairo_ps")
)
# suppress scientific notation
options(scipen = 999)
```
```{r info, echo = FALSE}
project_name <- "template" # adapt!
package_date <- "2018-12-01" # date of the CRAN snapshot that
# the checkpoint package uses
R_version <- "3.5.1" # R-Version to use
options(Ncpus = 4) # use 4 cores for parallelized installation of packages
if (R_version != paste0(version$major, ".", version$minor)){
  stop("ERROR: specified R version does not match currently used.")
}
```
```{r setup, echo=FALSE, include=FALSE}
source("install.R")
packages <- c(
  "tidyverse",
  "readr",
  "here",
  "tableone",
  "knitr",
  "kableExtra",
)
install(packages)
```

This report was generated on `r Sys.time()`. R version: `r paste0(version$major, ".", version$minor)` on `r version$platform`. For this report, CRAN packages as of `r package_date` were used.


```{r data input, echo = FALSE, message = FALSE, warning = FALSE }
data <- readr::read_csv(here::here("data", "faked_vims_data.csv"))
```

# Introduction

Here you should write a brief review of the literature with citations. You should cover enough to introduce the topic and make it clear why you are asking the questions that you are.

## Research Questions
1. Research Question 1
2. Research Question 2

## Hypotheses
1. Hypothesis 1
2. Hypothesis 2.

# Methods
Here you should outline the methods and give an overview of demographic information.

## Patients and Controls
>Patient and healthy control (HC) data were taken from an observational study, approved by the institutional review board (). HC matching patients for sex and age (+/-6 months) were identified using in-house python scripts using Python 3. Demograpic and clinical descriptive data are shown in Table 1.

```{r demographics, echo=FALSE}
age_diff <- with(data, t.test(age ~ diagnosis))
sex_diff <- chisq.test(table(data$sex, data$diagnosis))

vars = c(
  "age",
  "sex"
  )

knitr::kable(print(tableone::CreateTableOne(vars = vars, data = data, factorVars = "sex", strata = "diagnosis"), nonnormal = TRUE))
```

