---
output:
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./templates/svm-latex-ms.tex
  html_document:
    highlighting: tango
    keep_md: yes
    self_contained: yes
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: no
    fig_caption: yes
title: "Your project title here"
thanks: "Latex template taken from (https://github.com/svmiller/svm-r-markdown-templates)"
author:
- name: Your name
  affiliation: Neurocure Clinical Research Center, Charité Universitätsmedizin Berlin
- name: Someone else's name
  affiliation: Neurocure Clinical Research Center, Charité Universitätsmedizin Berlin
- name: Another person's name
  affiliation: Neurocure Clinical Research Center, Charité Universitätsmedizin Berlin
abstract: "Your abstract here"
keywords: "keywords here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
tables: true
link-citations: yes
bibliography: library.bib
biblio-style: apsr
---

```{r knitr options, echo = FALSE}
# set output directory and file type produced when "knitting""
knitr::opts_chunk$set(
  fig.path = here::here("figs"),
  screenshot.force = FALSE,
  dpi = 1200,
  dev = c("png", "jpeg", "cairo_ps")
)
```
```{r info, echo = FALSE}
project_name <- "template" 
package_date <- "2018-12-01" # date of the CRAN snapshot
R_version <- "3.5.1" # R-Version used
options(Ncpus = 4) # use 4 cores for parallelized installation of packages
if (R_version != paste0(version$major, ".", version$minor)){
  stop("ERROR: specified R version does not match currently used.")
}
# print sessonInfo() as markdown file
writeLines(capture.output(sessionInfo(package=NULL)), "sessionInfo.md")
```
```{r setup, echo=FALSE, include=FALSE}
# The following codes checks if required packages are installed, if not, installs them, and then loads them.
cranmirror <- "https://cran.cnr.berkeley.edu/"
if (!require(tidyverse)) {
  install.packages("tidyverse", repos = cranmirror); library(tidyverse)
  }
if (!require(dplyr)) {
  install.packages("dplyr", repos = cranmirror); library(dplyr)
  }
if (!require(readr)) {
  install.packages("readr", repos = cranmirror); library(readr)
  }
if (!require(stringr)) {
  install.packages("stringr", repos = cranmirror); library(stringr)
  }
if (!require(here)) {
  install.packages("here", repos = cranmirror); library(here)
  }
if (!require(lm.beta)) {
  install.packages("lm.beta", repos = cranmirror); library(lm.beta)
  }
if (!require(kableExtra)) {
  install.packages("kableExtra", repos = cranmirror); library(kableExtra)
  }
if (!require(cocor)) {
  install.packages("cocor", repos = cranmirror); library(cocor)
  }
if (!require(ggbeeswarm)) {
  install.packages("ggbeeswarm", repos = cranmirror); library(ggbeeswarm)
  }
if (!require(ggsignif)) {
  install.packages("ggsignif", repos = cranmirror); library(ggsignif)
  }
if (!require(stargazer)) {
  install.packages("stargazer", repos = cranmirror); library(stargazer)
}
if (!require(tableone)) {
  install.packages("tableone", repos = cranmirror); library(tableone)
  }
```
```{r external functions, echo=FALSE}
source(here::here("funcs", "print_p_value.R"))
```

> This report was generated on `r Sys.time()`. R version: `r paste0(version$major, ".", version$minor)` on `r version$platform`. For this report, CRAN packages as of `r package_date` were used. See "sessionInfo.md" file for detailed package information.

```{r data input, echo = FALSE, message = FALSE, warning = FALSE }
data <- readr::read_csv(here::here("data", "faked_vims_data.csv"))
```

# Introduction
Here you should write a brief review of the literature with citations. You should cover enough to introduce the topic and make it clear why you are asking the questions that you are.

## Research Questions
1. Research Question 1
2. Research Question 2

## Hypotheses
1. Hypothesis 1
2. Hypothesis 2.

# Methods
Here you should outline the methods and give an overview of demographic information.

## Patients and Controls
Patient and healthy control (HC) data were taken from an observational study, approved by the institutional review board (**INSERT ETHIC VOTE HERE**). HC matching patients for sex and age (+/-6 months) were identified using in-house python scripts using Python 3. Demograpic and clinical descriptive data are shown in Table 1.

```{r demographics, echo=FALSE, include=FALSE}
age_diff <- with(data, t.test(age ~ diagnosis))
sex_diff <- chisq.test(table(data$sex, data$diagnosis))

vars = c(
  "age",
  "sex"
  )

demographics_table <- knitr::kable(print(tableone::CreateTableOne(vars = vars, data = data, factorVars = "sex", strata = "diagnosis"), nonnormal = TRUE))
```

All patients and HC provided informed consent.

> *Table 1. Demographic information* `r demographics_table`.

## MRI Acquisition
MRI acquisition was performed on a 3 Tesla MRI (Tim Trio, Siemens Medical Systems, Erlangen, Germany). 

## MRI Analysis
Outline MRI analyses including software used.

## Statistical Analysis
### Confirmatory Analyses
Outline confirmatory statistical analysis (reference pre-registration). Highlight essential software packages.

### Exploratory Analyses
Outline any additional analysis that was not pre-registered. Highlight essential software packages.

## Results
### Demographics
No significant differences were found between MS and HC in sex ($\chi^2$ = `r sprintf("%.2f", sex_diff$statistic)` [`r sprintf("%.2f", sex_diff$parameter)`] *p* `r print_p_value(sprintf("%.3f", sex_diff$p.value), location= "text")`) or age
(*t* = `r sprintf("%.2f", age_diff$statistic)`, [`r sprintf("%.2f", age_diff$parameter)`] *p* `r print_p_value(sprintf("%.3f", age_diff$p.value), location = "text")`, 95% confidence interval `r sprintf("%.2f", age_diff$conf.int)`).

## Discussion


## Acknowledgements
We would like to thank all patients and healthy subjects who took part in the study. Further, we thank the study nurses, MRI technicians (S. Pikol and C. Kraut), and residents who aided in collecting the data. This work was supported by (**INCLUDE FUNDING BODY AND NUMBER**).

## References
